---
title: "MVPA_PTBUN_2023"
author: "Jacek Matuszewski"
date: '2023-09-15'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This script loads csv accuracy outputs from `runMVPA_unimodal_ReadSpeech.m` and 
plots individual accuracies + group mean & SE per decoding condition in each ROI. 

Expected structure: 
outputs
    derivatives
        cosmo-mvpa
            <decoding_label> [mostly atlas or ROI type, e.g. 'visfatlas']
                accuracies [this is where your csv files should be ]
                permutations [not important for this script]
                confusion matrices [not important for this script]


decoding condition = pairwise decoding between each par of classes
Script should work even if you only have 1 (e.g. multiclass decoding)

This script will also calculate "group summaries" for accuracy (mean se) and print 
them on plots for convenience

Looking for ROIs, conditions and sensory modalities is done through `unique` function, 
so it's not hardcoded, it will just look for the unique values in your analyses

Load packages
```{r Load Packages}
library(tidyverse)
library(data.table)
library(cowplot)
library(RColorBrewer)
library(patchwork)
library(stringr)
```


Set variables
```{r Setup variables}


ffx <- 'beta' # beta tmap
#featRatio <- '0.8' #just for saving outputs?
#space <-'IXI549Space'
FWHM <- 2
groups <- c('blind', 'sighted') # blind or sighted
# set te path to the task folder
stats_dir <- '/Volumes/Slim_Reaper/Projects/Language_MVPA/outputs/derivatives/bidspm-stats'

decoding_label <- 'cVWFA'#'visfatlas' #'cVWFA' 'LexPerVWFA' 'JuBrain'

roi_file_dir <- paste(stats_dir, 'derivatives','bidspm-groupStats', sep = '/')
roi_file_name <- paste0(decoding_label, '_stats.csv')

roi_fpath <- paste(roi_file_dir, roi_file_name, sep = '/')
```


Wrangle the ROI DF for plots

```{r DF wrangling and cleaning}
# EXPECTED STRUCTURE: LONG FORMAT WITH 1 COLUMN / ROI + 
# Condition, Group, Modality, Subject

# Get the raw csv file from MATLAB output and name the columns 
df.ROI.raw <- read_csv(roi_fpath, col_names = FALSE) %>% 
    rename(File = X1, 
           Group = X2, 
           ROI_file = X3, 
           Condition = X4, 
           ContrastEstimate = X5)

#Here you need to:
# 1. Extract the Subject ID from the file path - DONE
# 2. Extract the meaningfull non-BIDS ROI label from the BIDS name - DONE
# 3. Split the Condition into Condition and Modality on capital letter - DONE



df.ROI.clean <- df.ROI.raw %>% 
    #Get the subject name from file path
    mutate(Subject = str_split(File, "/", simplify = TRUE)[,9]) %>% 
    #Get the ROI label from ROI name
    # EXTRACT EVERYTHING BETWEENN _label- and next _
    mutate(ROI_label = str_match(ROI_file, "_label-\\s*(.*?)\\s*_")[,2]) %>% 
    #Get proper Condition and Modality names 
    group_by(Condition) %>% 
    mutate(Modality = unlist(str_split(Condition, "(?=[[:upper:]])"))[2]) %>% 
    mutate(Modality = recode(Modality, 'Read' = 'Reading')) %>% 
    mutate(Condition = unlist(str_split(Condition, "(?=[[:upper:]])"))[3]) %>% 
    ungroup() %>% 
    # Capitalize Group names for plotting functions 
    mutate(Group = sub("(.)", "\\U\\1", Group, perl=TRUE)) %>% 
    # Change condition names
     mutate(Condition = recode(Condition, 'Word' = 'Words', 
                               'Pseudoword' = 'Pseudowords')) %>% 
    # Drop the File and ROI_name from the df 
    dplyr::select(Subject, Group, Modality, Condition, ROI_label, ContrastEstimate)
    

```


Test to get labels
```{r}
#Can you find a way to get a ROI name between "label-" and "_" that works both for spheres and atlases?

# roi_atlas <- 'hemi-L_space-MNI_atlas-JuBrain_label-Broca_mask.nii'
# roi_sphere <- 'hemi-L_space-IXI549Space_label-cVWFA_radius-10mm_mask.nii'
# 
## ORIGINAL SOLUTION FROM STACK OVERFLOW
# a <- " anything goes here, STR1 GET_ME STR2, anything goes here"
# res <- str_match(a, "STR1\\s*(.*?)\\s*STR2")
# res[,2]
# 
# res_atlas <- str_match(roi_atlas, "_label-\\s*(.*?)\\s*_")[,2]
# res_roi <-str_match(roi_sphere, "_label-\\s*(.*?)\\s*_")[,2]

```


Summarize BOLD levels for descriptive purposes
```{r SUmmary Stats}
df.ROI.summaries <-  df.ROI.clean %>%
        group_by(Group, 
                 ROI_label,
                 Modality,
                 Condition) %>%
        dplyr::summarize(mean = mean(ContrastEstimate),
                                sd = sd(ContrastEstimate),
                                sem = sd(ContrastEstimate)/sqrt(n()),
                                .groups = 'keep')   
df.ROI.summaries
```


TEST BAR PLOTS WITH 1 FUNCTION FOR BOTH GROUPS!
```{r}
source('/Volumes/Slim_Reaper/Projects/Language_MVPA/code/src/cosmo-mpva/mvpa_plot_functions.R')

#For each roi in the DF 
roi_list <- unique(df.ROI.clean$ROI_label)

# make a bar plot with 2 groups and equal Y axes
for(i in seq_along(roi_list)){
    
    assign(paste0('plot.bar.roi.', roi_list[i]), 
           univariate_fMRI_ROI_bars_both_gr(df.ROI.clean, 
                                            roi = roi_list[i]))
}

```


TEST POINT PLOTS WITH 1 FUNCTION FOR BOTH GROUPS! 
```{r}
source('/Volumes/Slim_Reaper/Projects/Language_MVPA/code/src/cosmo-mpva/mvpa_plot_functions.R')

#For each roi in the DF 
roi_list <- unique(df.ROI.clean$ROI_label)

#TEST
#plot.point.test <- univariate_fMRI_ROI_points_both_gr(df.ROI.clean, roi = roi_list[1])

# make a bar plot with 2 groups and equal Y axes
for(i in seq_along(roi_list)){
    
    assign(paste0('plot.point.roi.', roi_list[i]), 
           univariate_fMRI_ROI_points_both_gr(df.ROI.clean, 
                                            roi = roi_list[i]))
}

```



Maybe add plot saving?

