---
title: "MVPA_PTBUN_2023"
author: "Jacek Matuszewski"
date: '2023-09-15'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load packages
```{r}
library(tidyverse)
library(data.table)
library(cowplot)
library(RColorBrewer)
library(patchwork)
```


Set variables
```{r}


ffx <- 'beta' # beta tmap
featRatio <- '0.8'
#space <-'IXI549Space'
FWHM <- 2
groups <- c('blind', 'sighted') # blind or sighted
# set te path to the task folder
cosmo_results <- '/Volumes/Slim_Reaper/Projects/Language_MVPA/outputs/derivatives/cosmo-mvpa'
#task_audVis <-  paste('task-audVisMotSpatialFreq_space-MNI152NLin2009cAsym_FWHM-', as.character(FWHM), '_node-mvpaBlockAverage', sep ='')
task_ReadSpeech <- paste0('task-MultimodalReadSpeech_space-IXI549Space_FWHM-',as.character(FWHM),'_node-mvpa6betas')

decoding_label <- 'visfatlas' #'cVWFA' 'LexPerVWFA'
cosmo_results_path_ReadSpeech <- paste(cosmo_results, task_ReadSpeech,  decoding_label,
                                       'unimodal','accuracy', sep ='/')

#namePattern <- paste('sub-',group,'.*_label-VWFAwithinmodal_.*\\.csv$', sep = '')
```


Load results and create group DFs
```{r}
for(g in seq_along(groups)) {
    
    #Set name pattern and get the files
    #namePattern <- paste('sub-',groups[g],'.*_label-VWFAwithinmodal_.*\\.csv$', sep = '')
    #namePattern <- paste('sub-',groups[g],'.*_label-VWFAcrossmodal_.*\\.csv$', sep = '')
    namePattern <- paste('sub-',groups[g],'.*_label-',decoding_label,'_.*\\.csv$', sep = '')
    
    allfiles_ReadSpeech <- list.files(cosmo_results_path_ReadSpeech, pattern = namePattern)
    
    group_df_temp <- lapply(paste(cosmo_results_path_ReadSpeech, 
                                  allfiles_ReadSpeech, sep ='/'), 
                            read.csv, sep =',') %>% 
        rbindlist %>% 
        dplyr::select(!contains('permutation')) %>% 
        mutate(accuracy = accuracy * 100) %>% #make %
        mutate(group = groups[g])#drop the null distribution columns %>%
    
        
    #Rename the group DF
    assign(paste0('mvpa_',groups[g]), group_df_temp)
    rm(group_df_temp)
}

#join the dfs
mvpa_joined <- rbind(mvpa_blind, mvpa_sighted)
rm(mvpa_blind, mvpa_sighted)

```


Specify plotting variables based on the MVPA content (ROIs, decoding conditions)
assumes identical variables between groups! 
```{r}
#Name of ROIs 
roi <- unique(mvpa_joined$roiArea)

#Name of decoding conditions 
classifier <- unique(mvpa_joined$conditions)
modalities <- unique(mvpa_joined$modality)
```

Summarize accuracies for descriptive purposes
```{r}
mvpa_accuracy <-  mvpa_joined %>%
        group_by(group, 
                 roiArea,
                 ffxResults,
                 modality,
                 conditions) %>%
        summarize(mean_accuracy = mean(accuracy),
                                sd_accurarcy = sd(accuracy),
                                se_accuracy = sd(accuracy)/sqrt(20),
                                .groups = 'keep')   
```


Plotting loop across everything? Start easy
```{r}

dark_colors <- brewer.pal(n=3, name = "Dark2") 
light_colors <- brewer.pal(n=3, name = "Pastel2") 
std.error <- function(x) sd(x)/sqrt(length(x))

for(g in seq_along(groups)) {
    for(m in seq_along(modalities)) {
       for(c in seq_along(classifier)) {
            for (r in seq_along(roi)) {

           plot <- 
                mvpa_joined %>% 
                # Pick a condition and modality for this plot
                filter(group == groups[g] & 
                           conditions == classifier[c] & 
                           modality == modalities[m] & 
                           ffxResults == ffx &
                           roiArea == roi[r]) %>% 
                ggplot(aes(x = roiArea, y = accuracy, color = roiArea)) +
                geom_point(aes(alpha = I(0.7)), 
                   position = position_jitterdodge(jitter.width=0.2,
                                                   dodge.width = 0.3),
                   size = 4.5) +
                stat_summary(aes(x = roiArea, y = accuracy, color = roiArea),
                     fun = "mean", 
                     geom = "crossbar", 
                     position = position_dodge(width = 0.5),
                     width = .55,
                     colour  = 'black',
                     inherit.aes = FALSE,
                    show.legend = FALSE) + 
                stat_summary(aes(x = roiArea, y = accuracy, color = roiArea),
                         fun.max = function(x) mean(x) + (std.error(x)), # sems too small for sighted
                         fun.min = function(x) mean(x) - (std.error(x)), # sems too small for sighted
                         #fun.max = function(x) mean(x) + sd(x),
                         #fun.min = function(x) mean(x) - sd(x),
                         geom = "errorbar",
                         position = position_dodge(width = 0.5),
                         width = .15,
                         size = 0.8,
                         colour  = 'black',
                         inherit.aes = FALSE,
                         show.legend = FALSE) + 
                geom_hline(yintercept=c(50), 
                       linetype="dotted", 
                       colour="black", 
                       linewidth=.5) +
                scale_color_manual(values = if(groups[g] == 'blind'){
                    c(dark_colors[1], light_colors[1])
                } else if(groups[g] == 'sighted') {
                    c(dark_colors[2], light_colors[2])
                }) +
                scale_y_continuous(name = "Clasisfier Accuracy [%]", 
                                   limits = c(0,100)) +
                scale_x_discrete(name = 'Region of interest', 
                                 labels = roi[r]) +
               # ggtitle(paste(groups[g], modalities[m], classifier[c], sep = ' ')) +
                theme_cowplot(font_size = 16, font_family = "Arial") +
                theme(axis.line = element_line(colour = 'black', size = 1),
                      axis.ticks = element_line(colour = 'black', size = 1),
                      axis.text = element_text(face="bold"),
                      legend.position = 'none')
                
                           
         
                                


            #Rename the plot based on what it represents 
            assign(paste('plot_unimodal',groups[g], classifier[c], roi[r], modalities[m],  
                         sep = '_'), plot)
            rm(plot)
            
            }
       }
   }
}

```


Pathwork plot pasting 
QUICK AND DIRTY, OPTIMIZE IT IN THE LOOP WHEN YOU HAVE FREE CODING TIME! 

V1
```{r}

plot_unimodal_blind_WordPseudoword_v1combined_reading + plot_unimodal_blind_WordControl_v1combined_reading + plot_unimodal_blind_PseudowordControl_v1combined_reading

plot_unimodal_sighted_WordPseudoword_v1combined_reading + plot_unimodal_sighted_WordControl_v1combined_reading + plot_unimodal_sighted_PseudowordControl_v1combined_reading


plot_unimodal_blind_WordPseudoword_v1combined_speech + plot_unimodal_blind_WordControl_v1combined_speech + plot_unimodal_blind_PseudowordControl_v1combined_speech

plot_unimodal_sighted_WordPseudoword_v1combined_speech + plot_unimodal_sighted_WordControl_v1combined_speech + plot_unimodal_sighted_PseudowordControl_v1combined_speech


```

iOS
```{r}

plot_unimodal_blind_WordPseudoword_IOS_reading + plot_unimodal_blind_WordControl_IOS_reading + plot_unimodal_blind_PseudowordControl_IOS_reading

plot_unimodal_sighted_WordPseudoword_IOS_reading + plot_unimodal_sighted_WordControl_IOS_reading + plot_unimodal_sighted_PseudowordControl_IOS_reading


plot_unimodal_blind_WordPseudoword_IOS_speech + plot_unimodal_blind_WordControl_IOS_speech + plot_unimodal_blind_PseudowordControl_IOS_speech

plot_unimodal_sighted_WordPseudoword_IOS_speech + plot_unimodal_sighted_WordControl_IOS_speech + plot_unimodal_sighted_PseudowordControl_IOS_speech


```


pOTS
```{r}

plot_unimodal_blind_WordPseudoword_pOTS_reading + plot_unimodal_blind_WordControl_pOTS_reading + plot_unimodal_blind_PseudowordControl_pOTS_reading

plot_unimodal_sighted_WordPseudoword_pOTS_reading + plot_unimodal_sighted_WordControl_pOTS_reading + plot_unimodal_sighted_PseudowordControl_pOTS_reading


plot_unimodal_blind_WordPseudoword_pOTS_speech + plot_unimodal_blind_WordControl_pOTS_speech + plot_unimodal_blind_PseudowordControl_pOTS_speech

plot_unimodal_sighted_WordPseudoword_pOTS_speech + plot_unimodal_sighted_WordControl_pOTS_speech + plot_unimodal_sighted_PseudowordControl_pOTS_speech


```



```{r}

## READING
#BLIND
plot_unimodal_blind_WordPseudoword_reading + plot_unimodal_blind_WordControl_reading + plot_unimodal_blind_PseudowordControl_reading
#SIGHTED
plot_unimodal_sighted_WordPseudoword_reading + plot_unimodal_sighted_WordControl_reading + plot_unimodal_sighted_PseudowordControl_reading

## SPEECH
#BLIND
plot_unimodal_blind_WordPseudoword_speech + plot_unimodal_blind_WordControl_speech + plot_unimodal_blind_PseudowordControl_speech
#SIGHTED
plot_unimodal_sighted_WordPseudoword_speech + plot_unimodal_sighted_WordControl_speech + plot_unimodal_sighted_PseudowordControl_speech

```

