---
title: "MVPA_PTBUN_2023"
author: "Jacek Matuszewski"
date: '2023-09-15'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This script loads csv accuracy outputs from `runMVPA_unimodal_ReadSpeech.m` and 
plots individual accuracies + group mean & SE per decoding condition in each ROI. 

Expected structure: 
outputs
    derivatives
        cosmo-mvpa
            <decoding_label> [mostly atlas or ROI type, e.g. 'visfatlas']
                accuracies [this is where your csv files should be ]
                permutations [not important for this script]
                confusion matrices [not important for this script]


decoding condition = pairwise decoding between each par of classes
Script should work even if you only have 1 (e.g. multiclass decoding)

This script will also calculate "group summaries" for accuracy (mean se) and print 
them on plots for convenience

Looking for ROIs, conditions and sensory modalities is done through `unique` function, 
so it's not hardcoded, it will just look for the unique values in your analyses

Load packages
```{r}
library(tidyverse)
library(data.table)
library(cowplot)
library(RColorBrewer)
library(patchwork)
```


Set variables
```{r}


ffx <- 'beta' # beta tmap
#featRatio <- '0.8' #just for saving outputs?
#space <-'IXI549Space'
FWHM <- 2
groups <- c('blind', 'sighted') # blind or sighted
# set te path to the task folder
cosmo_results <- '/Volumes/Slim_Reaper/Projects/Language_MVPA/outputs/derivatives/cosmo-mvpa'
#task_audVis <-  paste('task-audVisMotSpatialFreq_space-MNI152NLin2009cAsym_FWHM-', as.character(FWHM), '_node-mvpaBlockAverage', sep ='')
task_ReadSpeech <- paste0('task-MultimodalReadSpeech_space-IXI549Space_FWHM-',as.character(FWHM),'_node-mvpa6betas')

decoding_label <- 'JuBrain'#'visfatlas' #'cVWFA' 'LexPerVWFA' 'JuBrain'
#decoding_label <- 'cVWFA'#'visfatlas' #'cVWFA' 'LexPerVWFA' 'JuBrain'
cosmo_results_path_ReadSpeech <- paste(cosmo_results, task_ReadSpeech,  decoding_label,
                                       'unimodal','accuracy', sep ='/')

#namePattern <- paste('sub-',group,'.*_label-VWFAwithinmodal_.*\\.csv$', sep = '')
```


Load results and create group DFs
```{r}
for(g in seq_along(groups)) {
    
    #Set name pattern and get the files
    #namePattern <- paste('sub-',groups[g],'.*_label-VWFAwithinmodal_.*\\.csv$', sep = '')
    #namePattern <- paste('sub-',groups[g],'.*_label-VWFAcrossmodal_.*\\.csv$', sep = '')
    namePattern <- paste('sub-',groups[g],'.*_label-',decoding_label,'_.*\\.csv$', sep = '')
    
    allfiles_ReadSpeech <- list.files(cosmo_results_path_ReadSpeech, pattern = namePattern)
    
    group_df_temp <- lapply(paste(cosmo_results_path_ReadSpeech, 
                                  allfiles_ReadSpeech, sep ='/'), 
                            read.csv, sep =',') %>% 
        rbindlist %>% 
        dplyr::select(!contains('permutation')) %>% 
        mutate(accuracy = accuracy * 100) %>% #make %
        mutate(group = groups[g])#drop the null distribution columns %>%
    
        
    #Rename the group DF
    assign(paste0('mvpa_',groups[g]), group_df_temp)
    rm(group_df_temp)
}

#join the dfs
mvpa_joined <- rbind(mvpa_blind, mvpa_sighted) %>% 
    mutate(conditions = factor(conditions, levels = c('WordPseudoword', 'WordControl',
                                                      'PseudowordControl')))
rm(mvpa_blind, mvpa_sighted)

```


Specify plotting variables based on the MVPA content (ROIs, decoding conditions)
assumes identical variables between groups! 
```{r}
#Name of ROIs 
roi <- unique(mvpa_joined$roiArea)

#Name of decoding conditions 
classifier <- unique(mvpa_joined$conditions)
modalities <- unique(mvpa_joined$modality)
```

Summarize accuracies for descriptive purposes
```{r}
mvpa_accuracy <-  mvpa_joined %>%
     mutate(conditions = factor(conditions, levels = classifier)) %>% 
        group_by(group, 
                 roiArea,
                 ffxResults,
                 modality,
                 conditions) %>%
        summarize(mean_accuracy = mean(accuracy),
                                sd_accurarcy = sd(accuracy),
                                se_accuracy = sd(accuracy)/sqrt(20),
                                .groups = 'keep')   
```

PLOTTING FOR BOTH GROUPS (FUNCTIONS YOLO)
This chunk will produce one plot per ROI and modality, each ROI will have green-ish blind on the left and orangish sighted on the right. 
For future: consider what you will contrast (it should be on the same plot to mark interactions and significance)
Eg. MODALITY x GROUP interactions within ROIs should have both groups AND modalities on the same plot

```{r}

#Get some prerequisits
source('/Volumes/Slim_Reaper/Projects/Language_MVPA/code/src/cosmo-mpva/mvpa_plot_functions.R')
dark_colors <- brewer.pal(n=3, name = "Dark2") 
#light_colors <- brewer.pal(n=3, name = "Pastel2") 
std.error <- function(x) sd(x)/sqrt(length(x))


# HERE YOU ALSO HAVE MODALITIES!
for (m in seq_along(modalities)){
    for(r in seq_along(roi)){
        for(g in seq_along(groups)){
            
            #Slice the df to get given roi, group & modality
            plot_df <- mvpa_joined%>% 
                filter(roiArea == roi[r],
                       group == groups[g],
                       modality == modalities[m]) 
            
            #Slice the average summary df 
            accu_df <- mvpa_accuracy %>% 
                filter(group == groups[g] & 
                           modality == modalities[m] & 
                           ffxResults == ffx &
                           roiArea == roi[r])
            
            #make the basic plot with function
            plot_temp <- unimodal_mvpa_plot_ReadSpeech(plot_df, accu_df) 
            
            #recolour the plot based on group
            if (groups[g] == 'blind') {
                
                plot_temp <- plot_temp + 
                    scale_color_manual(values = c(rep(dark_colors[1], 3)))
                
            } else if (groups[g] == 'sighted') {
                
                plot_temp <- plot_temp + 
                    scale_color_manual(values = c(rep(dark_colors[2], 3)))
            }
            
            # assign new name to the sub plot 
            assign(paste0('plot_temp_', groups[g]), plot_temp)
            rm(plot_temp)
            
        }
        #PASTE THIS ROI AFTER BOTH GORUPS ARE DONE WITH PATCHWORK!
        plot_joined_temp <- plot_temp_blind + plot_temp_sighted
        
        assign(paste('plot_unimodal', roi[r], modalities[m], sep = '_'), plot_joined_temp)
        
        rm(plot_temp_blind, plot_temp_sighted, plot_joined_temp)
        
    }
}
```


SAVE THE PLOTS
```{r}
fig_dir <- paste(cosmo_results,task_ReadSpeech, decoding_label,'unimodal','plots/', sep = '/')

#Create an output dir - if it already exists R only prints a warning!
dir.create(fig_dir)
#Overrride the ggsave function to use white bg
ggsave <- function(..., bg = 'white') ggplot2::ggsave(..., bg = bg)

#List TMS grid plots
ggplot_list <- Filter(function(x) is(x, "ggplot"), mget(ls(pattern = "^plot_unimodal.*")))
plot_list <- ls(pattern = "^plot_unimodal_.*")

#Loop across main grids
for(i in seq_along(ggplot_list)) {

        ggsave(filename = paste0(fig_dir, plot_list[i], ".tiff"),
               plot = ggplot_list[[i]],
               units = "px",
               height = 320,
               width = 740,
               dpi = 300,
               scale = 5)
}
```

